Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Add missing article

In \term{Scantegrity}, public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

>>>>

In \term{Scantegrity}, the public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)
